{{< var titll >}}

### 2024-07-09 index.qmd
newpackges
upd

```{webr-r}
df <- ManifoldDestinyWASMD::yout
dplyr::select(df[[1]],S,T,U,V)
```

@@

```{webr-r}
# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
# ad
```

```{webr-r}
library(ggplot2)

# Create a sample data frame                                                                             
data <- data.frame(                                                                                      
  x = c(1, 2, 3, 4, 5),                                                                                  
  y = c(2, 3, 5, 7, 6)                                                                                   
)

# Create a scatter plot using ggplot2                                                                    
ggplot(data, aes(x = x, y = y)) + geom_point()                                                                                           
```

```{webr-r}
library(plotly)                                                                                          
# Create sample data                                                                                     
x <- seq(-5, 5, length.out = 100)                                                                        
y <- x                                                                                                   
z <- outer(x, y, function(x, y) cos(sqrt(x^2 + y^2)))

# Create 3D scatter plot                                                                                 
plot_ly(x = x, y = y, z = z, type = "scatter3d", mode = "markers")                                       
```

{{< audio file="abc.mp3" caption="Sample Audio File">}}

```{webr-r}
webr::mount(
  mountpoint = "/data",
  source = "https://example.com/output.data"
)
```

>>>>

```{webr-r}
dfl <- ManifoldDestinyWASMD::yout
df <- dplyr::select(dfl[[1]],S,T,U,V)
```

```{webr-r}
df
```

```{webr-r}
ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
ad
```

@@

### 2024-07-09 paper.qmd
upd

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
## {{< var sec2.un2 >}}
## {{< var sec2.un3 >}}
## {{< var sec2.un4 >}}
## {{< var sec2.un4 >}}

@@

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}
## {{< var sec6.un4 >}}

>>>>

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
## {{< var sec2.un2 >}}
## {{< var sec2.un3 >}}
## {{< var sec2.un4 >}}
## {{< var sec2.un5 >}}

@@

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

### 2024-07-09 presentation.qmd
upd

# {{< var sec1.nmn >}}
## {{< var sec1.un1 >}}
- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V

>>>>

## {{< var sec1.un1 >}}
- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V
